Opening up the court (surface) in tennis grand slams

### 2018-09-15 contest/surface-type/paper-tennis.Rmd
ideas for discussion

>>>>

+ HIGH LEVEL
  + in general point distribution seems to be the same, 
  + at the high level there are some surface differences that we have evidence for but cannot be sure either way: spainiards, 
  + there is no home court advantage 
  + French Open seems most different of the tournaments
  + country does not seem to have an effect but individual does with court
+ INTERMEDIATE LEVEL
  + Aces, Winners, and UEs are all important
  + Taller people have more aces
  + Wimbledon seems to have more winners and fewer UEs
+ LOW LEVEL
  + Hierarchical model doesnt show much effect for Nadal, Federer, and Williams
  + Individual models predicting % points won does show Nadal good on clay, fed on grass, and williams more jack of all trades
  + we have less info about higher ranked (worse) players -> we need more data to pick out these effects

+ FUTURE WORK:
  + closer look at point by point data
  + include other masters tournaments
  + pay more attention to year and players over time
